\begin{enumerate}[label=(\alph*)]
\item Contestant wins under the "stay-stay" strategy if and only if the Car is
behind Door $1$.

$$P(S) = \frac{1}{4}$$

\item If the Car is not behind Door $1$, Monty opens one of the two doors
revealing a Goat. Contestant stays. Then, Monty opens the other door with a Goat
behind it. Finally, contestant switches to the Door concealing the Car.

$$P(S) = P(C_{1})P(S|C_{1}) + P(C_{1}^{c})P(S|C_{1}^{c})$$

$$P(S) = 0 + \frac{3}{4} * 1 = \frac{3}{4}$$

\item Under the "switch-stay" strategy, if the Car is behind Door $1$ the
contestant loses. Given that the Car is not behind Door $1$, Monty opens one of
the Doors containing a Goat. The contestant will win if they switch to the Door
containing the Car and will lose if they switch to the Door containing the last
remaining Goat.

Thus,

$$P(S) = P(C_{1})P(S|C_{1}) + P(C_{1}^{c})P(S|C_{1}^{c}) = 0 + \frac{3}{4} * 
\frac{1}{2} = \frac{3}{8}$$

\item Under the "switch-switch" strategy, if the car is behind Door $1$, then
Monty opens a door with a Goat behind it. The contestant switches to a door
with a Goat behind it. Monty then opens the last door containing a Goat, at
which point the contestant switches back to the door containing the Car.

If Door $1$ contains a Goat, Monty opens another Door containing a Goat and
presents the contestant with a choice. If the contestant switches to the
remaining door containing a Goat, then Monty is forced to open Door $1$,
revealing the final Goat. The contestant switches to the one remaining Door
which contains the Car. If, on the other hand, the contestant switches to the
door containing the Car, then on the subsequent switch they lose the game.

Thus,

$$P(S) = \frac{1}{4}*1 + \frac{3}{4}* \frac{1}{2} = \frac{5}{8}$$

\item "Stay-Switch" is the best strategy.
\end{enumerate}