\begin{enumerate}[label=(\alph*)]
\item Let $X = \sum_{i=1}^{52}I_{i}$ be the number of cards that are called
correctly. $\text{E}(X) = \sum_{i=1}^{52}P(I_{i}=1) = 52\frac{1}{52} = 1$.

\item Source: \url{https://math.stackexchange.com/a/1078747/649082}

Let $X = \sum_{i=1}^{52}I_{i}$ be the number of cards that are
called
correctly. $\text{E}(X) = \sum_{i=1}^{52}P(I_{i}=1)$. To find $P(I_{i}=1)$,
consider the first $i$ cards, with the $i$-th card correctly guessed. Let
$k$ be the number of correctly guessed cards within the $i$ cards. For instance,
for $i=5$, $k=2$, $Y$ representing a correctly guessed card and $N$ representing
an incorrectly guessed card, one possible sequence of $i$ draws is $NYNNY$.

$$P(NYNNY) = \frac{51}{52}\frac{1}{51} \times \frac{50}{51}\frac{49}
{50}\frac{1}{49} = \frac{1}{52} \times \frac{1}{51}$$ Notice that
the second $N$ in the sequence has probability $\frac{50}{51}$,
because the second card is guessed correctly. The only piece
of information we have is that the third card is not the card that
was correctly guessed, leaving a total of $51$ possibilities. Generalizing, the
probability of a string of length $i$ with $k$ $Y$s is $\frac{(52-k)!}{52!}$.
There are $\binom{i-1}{k-1}$ strings of length $i$ with $k$ $Y$s that end in a
$Y$, and since $1 \leq k \leq i$, $$P(I_{i}=1) = \sum_{k=1}^{i}\binom{i-1}{k-1}
\frac{(52-k)!}{52!}$$

Thus,

\begin{align*}
\text{E}(X) &= \sum_{i=1}^{52}\sum_{k=1}^{i}\binom{i-1}{k-1}\frac{(52-k)!}{52!} \\
&= \sum_{k=1}^{52}\sum_{i=k}^{52}\binom{i-1}{k-1}\frac{(52-k)!}{52!} \\
&= \sum_{k=1}^{52}(\frac{(52-k)!}{52!}\sum_{i=k}^{52}\binom{i-1}{k-1}) \\
&= \sum_{k=1}^{52}(\frac{(52-k)!}{52!}\binom{52}{k}) \\
&= \sum_{k=1}^{52}\frac{1}{k!}
\end{align*}

Note that $e^{x} = \sum_{i=0}^{\infty}\frac{x^{i}}{i!} \implies e^{1} \approx 1
+
\text{E}(X) + 10^{-15}$. Thus, $$\text{E}(X) \approx e - 1$$.

\item Since at any given time, we know all the cards remaining in the deck, the
probability of the $i$-th card being the card guessed correctly is $\frac{1}
{52-i+1}$. Thus, $\text{E}(X) = \sum_{i=1}^{52}\text{E}(I_{i}) = \sum_{i=1}^{52}P
(I_{i}=1) = \sum_{i=1}^{52}\frac{1}{52-i+1} = \sum_{i=0}^{51}\frac{1}{52-i}
\approx 4.54$.
\end{enumerate}